\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Ye Lin Aung}}\\
	Singapore $\cdot$ me@yelinaung.com $\cdot$ +6597806044 $\cdot$ www.yelinaung.com\\
\end{center}

%==== Experience ====%
\header{Employment}
\vspace{1mm}

\textbf{99 Group} \hfill Singapore\\
\textit{Chief Software Architect} \hfill Nov 2021 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Help multiple product teams align their work with long-term business objectives and oversee their architecture and implementation.
	\item Lead the 99 Group infrastructure team of 5 people (and growing). Work with the CTO to plan the roadmaps. Work with the team members to plan the tasks long-term.
	\item Work with the engineering team leads across multiple pillars (frontend, backend, etc) to plan the engineering road-maps.
	\item Hands-on implementation to improve the development and CI/CD process. Resulting in better workflow and 50 \% reduce in build time.
	\item Implemented all cost-saving efforts resulting in a 20 \% reduction in bills in the quarter.
	\item Involve and architect the design/infrastructure of the expansion of the site to another country.
\end{itemize}
\textbf{99 Group} \hfill Singapore\\
\textit{Backend and Infra Lead (Senior Software Engineer)} \hfill April 2020 - Nov 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Lead both backend and infrastructure pillars of 99.co Singapore Team. Responsible for designing the APIs and microservices. Grew the team from 6 members to 12 members.
	\item Maintain the infrastructure on Kubernetes (with GKE), CloudBuild, and CloudSQL. Implemented application-level latency monitoring with Prometheus and dashboards + alerts in Grafana. Resulting in better insights, ability to proactively mitigating the issues and helping to prioritize the roadmaps.
	\item Migration of the legacy Infra on AWS (RDS, EC2) to GCP, resulting in an increase in productivity and reduction in billing (est 20\% drop in total bill).
	\item Supervised a mix of junior and mid-level engineers (up to 15 members) by mentoring and conducting regular 1-1s with them, listening to them, and providing feedback.
\end{itemize}
\textbf{99 Group} \hfill Singapore\\
\textit{Full Stack Software Engineer} \hfill March 2016 - March 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed 99.co Singapore Android application
	\item Worked on 99.co Indonesia backend/data import/API/client Android app
	\item Shift to focus on the 99.co Backend services
	\item Developed a critical service: Subscription and Wallet System by using Python, Tornado, Mongo, Redis. Subscription service is a critical part of the business. As part of the subscription service, developed the internal (coin) wallet system to allow people to buy and spend on items on the 99.co website such as boosting the property listings.
\end{itemize}
\textbf{Zwenexsys Intl Ltd} \hfill Yangon, Myanmar\\
\textit{Software Engineer} \hfill Jan 2013 - Dec 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Responsible to support and handling the general software/hardware problems.
	\item Assigned to work on standalone projects
\end{itemize}

%==== Education ====%
\header{BSc Hons (Business Information Technology)}
\textbf{University of Greenwich}\hfill London, England\\
BSc Business Information Technology \hfill 2010 - 2013\\
\vspace{2mm}

\header{Technical Skills}
\begin{tabular}{ l l }
	Technologies:          & Git, Kubernetes, Docker, Linux, Terraform, GCP, AWS, Istio, Nginx, CI/CD Tools \\
	Programming Languages: & Python, Bash, Java, Kotlin, YAML, SQL.                                         \\
	Databases:             & PostgreSQL, MongoDB, Redis, ElasticSearch                                      \\
\end{tabular}
\vspace{2mm}

\header{Certificates}
\textbf{Certified Kubernetes Application Developer (CKAD)} \hfill Linux Foundation\\
\hfill 2021\\
\vspace*{2mm}
\textbf{Certified Kubernetes Administrator (CKA)} \hfill Linux Foundation\\
\hfill 2022\\
\vspace*{2mm}



\ 
\end{document}